Contextual Combinatorial Cascading Bandits

### 2015-12-08 contextual combinatorial cascading bandits.tex

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
	\label{eq:functionf}
\end{align}
Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
\begin{align*}
A_t^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
f_t^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R(T) = \EE[\sum_{t=1}^T R(t, \bA_t)].
$$
where $R(t, \bA_t) = f_t^{\ast} - f(\bA_t, \theta_{\ast}^{\top}x_t)$.

@@

If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
\begin{align}
&f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)
 (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
 \label{eq:functionfstar}
\end{align}
then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. To simplify notations, we assume 
$$
\gamma_k' = 1 - \gamma_k.
$$
Then it holds that
\begin{equation}
\label{eq:ConDisRelation}
f_{\wedge}(A, w) = 1 - f(A, 1 - w).
\end{equation}
Let 
\begin{align*}
A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R_{\wedge}(T) = \EE[\sum_{t=1}^T R_{\wedge}(t, \bA_t)].
$$
where $R_{\wedge}(t, \bA_t) = f_{\wedge, t}^{\ast} - f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$.

@@

The next lemma provides some properties about a prefix of action $A$
	in the conjunctive case, 
	which leads to the finding of a prefix $B$ of $A$ with similar regret
	and probability of full observation as those of $A$, as given
	in Lemma~\ref{lem:prefixexists}.
\begin{lemma}
\label{lem:prefixRelation}
Suppose 
% $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and 
$0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
% For the conjunctive case, it holds that
% $$
% p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
% $$
Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. 
\wei{$p_{\wedge, A}$ is not defined before. Only $p_{\wedge, t, A}$ is defined.
	I guess you are using $w$ vector to be the mean vectors for $A$. Please define
	this clearly.}
\shuai{I have modified this part.}
Suppose we have weights $w$. Let $p_{\wedge, A}$ be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the conjunctive objective:
$$
p_{\wedge, A} = \prod_{k=1}^{\abs{A}-1} w_{a_k}.
$$
Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
\begin{itemize}
\item[(1)] $f_{\wedge}(A, w) \leq \gamma_{\abs{A}}' + (1 - \gamma_{\abs{A}}') p_{\wedge, A}$;
\item[(2)] $f_{\wedge}(B_{k+1}, w) \leq f_{\wedge}(B_k, w)$;
\item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}$.
\end{itemize}
\end{lemma}

\begin{proof}
% It suffices to prove these properties when $A = A^{(m)}$ and $w = (w_1, \ldots, w_m)$. First, for the conjunctive objective,
% $$
% f(A, w) \geq \gamma_{m} (1 - p_{A} + p_{A} w_{m}) \geq \gamma_{m} (1 - p_{A}).
% $$
% Then for the disjunctive objective,
\begin{itemize}
\item[(1)]
\begin{align*}
f_{\wedge}(A, w) &\leq \gamma_m'(1 - p_{\wedge, A} w_m) + p_{\wedge, A} w_m \\
&\leq \gamma_m' + (1 - \gamma_m') p_{\wedge, A};
\end{align*}

@@

\item[(4)]
\begin{align*}
f_{\wedge}(B_k, w) &\leq \gamma_{k}' (1 - p_{B_{k+1}}) + p_{B_{k+1}}\\
&\leq \gamma_{k+1}' (1 - p_{B_{k+1}}) + p_{B_{k+1}} \\
&= \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}
\end{align*}
\end{itemize}
\end{proof}

\begin{lemma} \label{lem:prefixexists}
Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
$$
p_{\wedge, t, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
$$ 
\end{lemma}
\begin{proof}
If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation},
$$
p_{\wedge, t, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
$$

Suppose $f_{\wedge}(A, w) \leq \frac{1}{2} f_{\wedge, t}^{\ast}$. Let
$$
x_k = f_{\wedge}(B_k,w), ~~ y_k = \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}, ~~I_k = [x_k, y_k]
$$
Then by Lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$. Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$. Also, $x_{\abs{A}} = f_{\wedge}(A, w)$ and $y_1 = 1$. Thus
$$
[f_{\wedge}(A,w), 1] = \bigcup_{k=1}^{\abs{A}} I_k.
$$
Then there exists a $k$ such that $\frac{1}{2}f_{\wedge, t}^{\ast} \in I_k$:
$$
f_{\wedge}(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{\wedge, t, B_k}
$$
Therefore, the results are derived.
\end{proof}

\begin{lemma}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
$$
E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \EE[ \beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} ].
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \EE[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}].
\end{align*}
\end{lemma}
\begin{proof}
For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$. Then we have
$$
\EE_t[R_{\wedge}(t, \bA_t)] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[R_{\wedge}(t, \bB_t) \bOne\{R_{\wedge}(t, \bB_t) > 0, \bO_t \geq \abs{\bB_t}\}]
$$
Because 
$$
f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
$$
by Lemma \ref{lem:increasing} and
$$
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
by Lemma \ref{lem:estimateTech}, we have
$$
R_{\wedge}(t, \bB_t) \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore
\begin{align*}
\EE_t[R_{\wedge}(t, \bA_t)] &\leq \EE[\frac{8}{f_{\wedge, t}^*} \bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq \EE[ \frac{8}{f_{\wedge}^*} \sum_{k=1}^{ \bO_t } \beta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} ]
\end{align*}
\end{proof}

\begin{lemma} % det(V_t)
$\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
\end{lemma}
\begin{proof}
We have $\det(\bV_t) \leq (\trace(\bV_t)/d)^d$ and
\begin{align*}
&\trace(\bV_t)\\
& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \norm{x_{s,\ba_k^s}}_2^2\\
& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k^2 = d \lambda + t C_\gamma.
\end{align*}
\end{proof}

@@

\begin{lemma}
If $\lambda \geq C_\gamma$, then
$$
\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln(\frac{\det(\bV_t)}{\lambda^d}).
$$
\end{lemma}
\begin{proof}
\begin{align*}
&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k X_{t,\ba_k^{t}})(\gamma_k X_{t, \ba_k^{t}}^{\top}))\\
&=\det(\bV_{t-1})\\
&~~~\cdot \det(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
\end{align*}
Because
$$
\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
$$
we have 
$$
\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
$$
Using the fact that $ 2\ln(1+u) \geq u$ for any $u \in [0,1]$, we get
\begin{align*}
&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
&\leq 2\sum_{s=1}^t\ln(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
&\leq 2(\ln(\det(\bV_t)) - \ln(\det(\lambda I))) \\
&= 2 \ln(\frac{\det(\bV_t)}{\det(\lambda I)})
\end{align*}
\end{proof}

@@

For the conjunctive case,
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \\
&\leq \EE[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t[\beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]]\\
&\leq \EE[\frac{1}{p^*} \beta_T(\delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]} ]  \\
&\leq \EE[\frac{1}{p^*} (\sqrt{\ln(\frac{\det(\bV_t)}{\det(\lambda I)}) + 2\ln(\frac{1}{\delta})} + \sqrt{\lambda}) \\
&\qquad \qquad \cdot \sqrt{TK \cdot 2\ln(\frac{\det(\bV_t)}{\det(\lambda I)})} ]\\
&\leq \frac{\sqrt{2}}{p^*} (\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln(\frac{1}{\delta})} + \sqrt{\lambda})\\
&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
\end{split}
\end{equation}

>>>>

Now let us introduce a function $f$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{align}
&f : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k).
	\label{eq:functionf}
\end{align}
Then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
\begin{align*}
A_t^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
f_t^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R(T) = \EE\left[\sum_{t=1}^T R(t, \bA_t)\right].
$$
where $R(t, \bA_t) = f_t^{\ast} - f(\bA_t, \theta_{\ast}^{\top}x_t)$.

@@

If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
\begin{align}
&f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)
 (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
 \label{eq:functionfstar}
\end{align}
then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. To simplify notations, we assume 
$$
\gamma_k' = 1 - \gamma_k.
$$
Then it holds that
\begin{equation}
\label{eq:ConDisRelation}
f_{\wedge}(A, w) = 1 - f(A, 1 - w).
\end{equation}
Let 
\begin{align*}
A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
$$
where $R_{\wedge}(t, \bA_t) = f_{\wedge, t}^{\ast} - f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$.

@@

The next lemma provides some properties about a prefix of action $A$
	in the conjunctive case, 
	which leads to the finding of a prefix $B$ of $A$ with similar regret
	and probability of full observation as those of $A$, as given
	in Lemma~\ref{lem:prefixexists}.
\begin{lemma}
\label{lem:prefixRelation}
Suppose 
% $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and 
$0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
% For the conjunctive case, it holds that
% $$
% p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
% $$
Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. 
Suppose we have expected weights $w$ for the base arms of action $A$. 
Let $p_{\wedge, A}$ be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the conjunctive objective:
$$
p_{\wedge, A} = \prod_{k=1}^{\abs{A}-1} w_{a_k}.
$$
Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
\begin{itemize}
\item[(1)] $f_{\wedge}(A, w) \leq \gamma_{\abs{A}}' + (1 - \gamma_{\abs{A}}') p_{\wedge, A}$;
\item[(2)] $f_{\wedge}(B_{k+1}, w) \leq f_{\wedge}(B_k, w)$;
\item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{\wedge,B_{k+1}}$.
\end{itemize}
\end{lemma}

\begin{proof}
% It suffices to prove these properties when $A = A^{(m)}$ and $w = (w_1, \ldots, w_m)$. First, for the conjunctive objective,
% $$
% f(A, w) \geq \gamma_{m} (1 - p_{A} + p_{A} w_{m}) \geq \gamma_{m} (1 - p_{A}).
% $$
% Then for the disjunctive objective,
Let $m = |A|$.
By the definition of $f_{\wedge}(A,w)$ in Eq.~\eqref{eq:functionfstar}, we have
\begin{itemize}
\item[(1)]
\begin{align*}
	f_{\wedge}(A,w) & = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)
	(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i) \\
 &\leq \gamma_m'(1 - p_{\wedge, A} w_m) + p_{\wedge, A} w_m \\
&\leq \gamma_m' + (1 - \gamma_m') p_{\wedge, A};
\end{align*}

@@

\item[(4)]
\begin{align*}
f_{\wedge}(B_k, w) & \leq \gamma_{k}' (1 - p_{\wedge,B_{k+1}}) + p_{\wedge,B_{k+1}}\\
&\leq \gamma_{k+1}' (1 - p_{\wedge,B_{k+1}}) + p_{\wedge,B_{k+1}} \\
&= \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{\wedge,B_{k+1}}
\end{align*}
\end{itemize}
\end{proof}

\begin{lemma} \label{lem:prefixexists}
Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
$$
p_{\wedge, t, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
$$ 
\end{lemma}
\begin{proof}
Let $w= \theta_*^{\top} x_t$.
If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation} (1),
$$
p_{\wedge, t, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
$$
In this case, we set prefix $B = A$.

Now suppose $f_{\wedge}(A, w) \leq \frac{1}{2} f_{\wedge, t}^{\ast}$. Let
$$
x_k = f_{\wedge}(B_k,w), ~~ y_k = \gamma_k' + (1 - \gamma_k')p_{\wedge, t,B_k}, ~~I_k = [x_k, y_k]
$$
Then by Lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$. Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$. Also, $x_{\abs{A}} = f_{\wedge}(A, w)$ and $y_1 = 1$. Thus
$$
[f_{\wedge}(A,w), 1] = \bigcup_{k=1}^{\abs{A}} I_k.
$$
Then there exists a $k$ such that $\frac{1}{2}f_{\wedge, t}^{\ast} \in I_k$:
$$
f_{\wedge}(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{\wedge, t, B_k}
$$
Therefore, the results are derived.
\end{proof}

\wei{This lemma needs to be clarified, using Lemma 4.6.
Also, our regret bound is expected regret but with a high probability? Sound a 
bit strange.}
\begin{lemma}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
$$
E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \EE\left[ \beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \EE\left[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right].
\end{align*}
\end{lemma}
\begin{proof}
For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$. Then we have
$$
\EE_t[R_{\wedge}(t, \bA_t)] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[R_{\wedge}(t, \bB_t) \bOne\{R_{\wedge}(t, \bB_t) > 0, \bO_t \geq \abs{\bB_t}\}]
$$
Because 
$$
f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
$$
by Lemma \ref{lem:increasing} and
$$
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
by Lemma \ref{lem:estimateTech}, we have
$$
R_{\wedge}(t, \bB_t) \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore
\begin{align*}
\EE_t[R_{\wedge}(t, \bA_t)] &\leq \EE \left[\frac{8}{f_{\wedge, t}^*} \bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
&\leq \EE \left[ \frac{8}{f_{\wedge}^*} \sum_{k=1}^{ \bO_t } \beta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]
\end{align*}
\end{proof}

\begin{lemma} % det(V_t)
$\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.$
\end{lemma}
\begin{proof}
We have $\det(\bV_t) \leq (\trace(\bV_t)/d)^d$, 
\wei{Why? need a citation?} and
\begin{align*}
&\trace(\bV_t)\\
& = \trace(\lambda I) + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \trace(x_{s,\ba_k^s} x_{s,\ba_k^s}^{\top})\\	
& = d \lambda + \sum_{s=1}^t \sum_{k=1}^{\bO_s} \gamma_k^2 \norm{x_{s,\ba_k^s}}_2^2\\
& \leq d \lambda + \sum_{s=1}^t\sum_{k=1}^{K}\gamma_k^2 = d \lambda + t C_\gamma.
\end{align*}
\end{proof}

@@

\begin{lemma}
If $\lambda \geq C_\gamma$, then
$$
\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
$$
\end{lemma}
\begin{proof}
\begin{align*}
&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k X_{t,\ba_k^{t}})(\gamma_k X_{t, \ba_k^{t}}^{\top}))\\
&=\det(\bV_{t-1})\\
&~~~\cdot \det(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
\end{align*}
Because
$$
\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
$$
we have 
$$
\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
$$
Using the fact that $ 2\ln(1+u) \geq u$ for any $u \in [0,1]$, we get
\begin{align*}
&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
&\leq 2\sum_{s=1}^t\ln(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
&\leq 2(\ln(\det(\bV_t)) - \ln(\det(\lambda I))) \\
&= 2 \ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right)
\end{align*}
\end{proof}

@@

For the disjunctive case,
\begin{equation}
\begin{split}
&R(T) =\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \\
&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right]\\
&\leq \EE \left[\frac{1}{p^*} \beta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \EE \left[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right]}
	\right ]  \\
&\leq \EE\left[\frac{1}{p^*} \left(\sqrt{\ln \left(\frac{\det(\bV_t)}{\det(\lambda I)}\right) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda} \right) \right. \\
& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_t)}{\det(\lambda I)} \right)} \right]\\
&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln \left(\frac{1}{\delta} \right)} + \sqrt{\lambda} \right)\\
&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} ]
\end{split}
\end{equation}
